Allee Effect and Cultural Evolution

### 2015-05-29 manuscript/draft.tex
updated tex

\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figure3.pdf}
  \caption{Basins of attraction for the four equilibria (mutual extinction: grey; extinction of $a$: blue; extinction of $b$: red; stable coexistence: green) with (right) and without (left) social learning. Model parameters: $A_a=0.2$; $K_a=0.8$; $A_b=0.4$; $K_b=1.0$; $r_a=r_b=0.05$; $z=0$ (left panel) and $z=0.05$ (right panel) }
    \label{fig:TransmissionBasin}
\end{figure}

@@

The dynamics of two strategies are similar for low values of $\lambda$. High values indicate that the minimum number of individuals needed to achive positive fitness in $b$ gets closer to $K_a$, while the population size that $b$ can sustain also grows. As a consequence, the number of individuals switching strategies when $b$ has lower payoff is also higher and could potentially overload $a$ due to its lower $K_a$.

Figure XX shows how the increase in $\lambda$ affects the equilibria of our model.

% XAVI add results and figure

@@

Figure XX shows a scenario where strategy $a$ is dominant over strategy $b$.
% XAVI add results and figure

>>>>

% XAVI put high res figure
\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figure3.pdf}
  \caption{Basins of attraction for the four equilibria (mutual extinction: grey; extinction of $a$: blue; extinction of $b$: red; stable coexistence: green) with (right) and without (left) social learning. Model parameters: $A_a=0.2$; $K_a=0.8$; $A_b=0.4$; $K_b=1.0$; $r_a=r_b=0.05$; $z=0$ (left panel) and $z=0.05$ (right panel) }
    \label{fig:TransmissionBasin}
\end{figure}

@@

The dynamics of two strategies are similar for low values of $\lambda$. High values indicate that the minimum number of individuals needed to achieve positive fitness in $b$ gets closer to $K_a$, while the population size that $b$ can sustain also grows. As a consequence, the number of individuals switching strategies when $b$ has lower payoff is also higher and could potentially overload $a$ due to its lower $K_a$.

Figure \ref{fig:overlap} shows how the degree of overlap affects the equilibria of our model with and without social learning. The relation between the two processes strongly affects the shape of the different basins in a non-dynamic fashion.

% XAVI put high res figure, and update left, middle, right order

\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figure5}
  \caption{Basins of attraction for $z=0.05$ (top) and $z=0.2$ (bottom); $\lambda=1$ (left), $\lambda=0.75$ (middle) and $\lambda=0.5$}
    \label{fig:overlap}
\end{figure}

Figure \ref{fig:percentages} explores in deeper detail the effects of both parameters ($z$ and $lambda$) on the basin of each equilibria. An increase in $z$ decreases the possibility of having coexistence for high similarity between strategies $a$ and $b$ (i.e. $\lambda \geq 0.9$. From $0.9 < \lambda < 0.55$ the dynamics remain remarkably similar, while for $\lambda = 0.5$ the effects of social learning decreases because of the large gap between $A$ and $K$ of both strategies.

\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figure6}
  \caption{Percentages of the entire space falling in each basin of attraction for different values of $\lambda$. X axis controls the parameter $z$ defining social learning.}
    \label{fig:percentages}
\end{figure}

@@

Figure \ref{fig:competition} shows a scenario where strategy $a$ is dominant over strategy $b$.

\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figure7}
  \caption{The impact of competition on the basins of attraction for the different equilibria. The Parameters used are $z=0.05$ (left) and $z=0.2$ (right) for social learning, and $c=-0.1$ (top) and $c=0.1$ (bottom) for competition.}
    \label{fig:competition}
\end{figure}

% XAVI some brief discussion on results here, and update the dashed lines
